\documentclass[fontsize=10pt]{tccv}
\usepackage[english]{babel}
\usepackage{fontawesome} % disable font-awesome speed up A LOT
% \usepackage[compact]{titlesec} fail

\begin{document}

\part{Pinglei Guo}

\section{Work experience}

\begin{eventlist}

% use fontawesome icon, see fontawesome.pdf and fontawesome.tex for detial
% \faCheck

% TODO: reduce the margion
% TODO: reduce font size
% \item{January 2015 -- March 2015}
%      {GitCafe, Shanghai, China}
%      {Software Engineer (Ruby on Rails)}

\textit{January 2015 -- March 2015} \\
\textbf{Software Engineer}, GitCafe, Shanghai, China \smallskip

Optimize ruby markdown parser.
Fix encoding problem in rugged.
Improve user subscription logic.

\medskip

% \item{September 2013 -- January 2015}
%      {Dongyue Web Studio, Shanghai, China}
%      {Full stack web developer}

\textit{September 2013 -- January 2015} \\
\textbf{Full stack web developer}, Dongyue Web Studio, Shanghai, China\smallskip

Build RESTful API and microservice using modern PHP, NodeJS frameworks like Laravel, Express.
Develop responsive user interface using Bootstrap and AngularJS.
Build internal tools for continuous integration, monitoring and alert.
Build user recommendation system based on PredictionIO.

\end{eventlist}

\section{Research Experience}

\begin{eventlist}

% \item{March 2015 -- November 2015}
%      {Shanghai Jiao Tong University, China}
%      {Research Assistant}

\textit{March 2015 -- November 2015} \\
\textbf{Research Assistant}, Shanghai Jiao Tong University, China\smallskip

Build a distributed system monitoring and prediction prototype.
Metrics visualizing dashboard using AngularJS and WebSocket, support real time update and custom plugin.
Implement a plain text protocol for data transport and collector control using Netty.
Coauthored the paper \textit{CPU load Prediction based on a multidimensional spatial voting model}.

\medskip

% \item{July 2015 -- September 2015}
%      {Victoria University, Australia}
%      {Research Assistant}

\textit{July 2015 -- September 2015} \\
\textbf{Research Assistant}, Victoria University, Australia\smallskip

% TODO: better wording
% http://www.aie.org/find-a-job/write-your-resume/100-great-resume-words.cfm
% http://www.monster.com/career-advice/article/10-words-ruin-resume
Estimate Australian Football League Sports men's commercial value.
Build a web crawler embedded into ASP.NET web application to get performance.
Using text mining to get evaluation from social media and press.
Combine athlete's performance with evaluation to generate rank and estimated value.

\end{eventlist}

% TODO: maybe another name?
\section{Project Experience}

\begin{eventlist}

% \item{March 2015 -- June 2015}
%      {Project Leader}
%      {Scala linter}

\textit{November 2015 -- January 2016} \\
\textbf{B+ index for Hive} \textit{Project leader}\smallskip

Build and store B+ index for Hive.
Support point and range query with built in cache using memory or Redis.
Dashboard and API using AngularJS and Spring framework.

\medskip

\textit{October 2015 -- December 2015} \\
\textbf{Search Engine based on Hadoop} \textit{Project leader}\smallskip

Build multithread crawler to abstract data from forums.
Use Map-Reduce to generate inverted index and store in HDFS.
Provide REST API using Spring framework.

\medskip

\textit{March 2015 -- June 2015} \\
\textbf{Scala linter} \textit{Project leader}\smallskip

Build Scala compiler plugin to check dead code.
Contributed to Scala official documentation.

\medskip

% \item{September 2013 -- January 2014}
%      {Project Leader}
%      {Real time route control based on image processing}

\textit{September 2013 -- January 2014} \\
\textbf{Real time route control for toy car} \textit{Project leader}\smallskip

Use OpenCV to extract car position from real time image.
Generate and optimize route.
Control the car using single chip machine via bluetooth.
A standalone GUI application using MFC for configuration and
real time monitor.

% TODO: the btree project or search engine project

\end{eventlist}


% TOD: better icon and links to github, linkedin
\begin{figure}[t] % Push the figure at the bottom; use t for top
% \personal[www.entidi.com]
%       {viale Conciliazione, 13\newline 25039 -- Travagliato (BS)}
%       {+39 (30) 6862332}
%       {ntd@entidi.it}
\begin{tabularx}{\dimexpr\linewidth-2\fboxsep\relax}{cX}
% TODO: pdfnewwindow is not working http://tex.stackexchange.com/questions/200577/make-hyperref-links-open-in-new-browser-window-for-easier-navigation
\faHome & \href{https://at15.github.io}{at15.github.io}\smallskip\\
\faEnvelope& \href{mailto:at15@outlook.com}{at15@outlook.com}\smallskip\\
\faGithub & \href{https://github.com/at15}{at15}\smallskip\\
\faLinkedin & \href{https://www.linkedin.com/in/at1510086}{at1510086}\smallskip\\

\end{tabularx}
\end{figure}

\section{Education}

\begin{yearlist}

\item{2016 -- Present}
     {MS. Computer Science}
     {University of California Santa Cruz}

\item{2012 -- 2016}
     {BS. Material Science}
     {Shanghai Jiao Tong University, China}

\item{2013 -- 2016}
    {BA. Animation}
    {Shanghai Jiao Tong University, China}

\end{yearlist}

\section{Open source project}

\begin{factlist}

\item{Ayi}
     {\href{https://github.com/dyweb/Ayi}{A cross platform util application written in Golang}}

\item{About}
    {\href{https://github.com/tongquhq/about}{Blog and static site generator for individual and team in Node.js}}

\item{Linter}
    {\href{https://github.com/at15/scala-linter}{Scala dead code detection compiler plugin}}

\item{DyGroup}
    {\href{https://coding.net/u/arrowrowe/p/dyGroup/git}{A slack alternative, IM and collaboration platform for team}}

\end{factlist}

% TODO: do I really need this
% \section{Communication skills}
%
% \begin{factlist}
% \item{Chinese}{Native speaker}
% \item{English}{Oral: fair -- Written: good}
% \end{factlist}

\section{Programming Language}

\begin{factlist}

\item{Experienced}
     {JavaScript, PHP, HTML, CSS, MATLAB}

\item{Intermediate}
     {Golang, Java, Ruby, Python, SQL}

\item{Basic level}
     {C, Scala, shell}

\end{factlist}

\section{Software \& Frameworks}

\begin{factlist}

\item{Experienced}
     {Git, AngularJS, jQuery, D3.js, Bootstrap, Laravel, Express}

\item{Intermediate}
     {MySQL, Redis, Rails, Cinema4D, Photoshop}

\item{Basic level}
     {Docker, Nginx, Hadoop, HBase, Hive}

\end{factlist}

% \section{Publication}

\end{document}
