\documentclass[11pt, letterpaper]{simple-cv}
% https://github.com/at15/at15.github.io/issues/10 to solve LaTeX Font Warning: Font shape `TU/ptm/m/n' undefined
% https://tex.stackexchange.com/questions/358261/latex-font-warning-after-updating-to-texlive-2016/
\usepackage[OT1]{fontenc} 
% to use times new roman https://tex.stackexchange.com/questions/153168/how-to-set-document-font-to-times-new-roman-by-command
\usepackage{mathptmx}
\usepackage{enumitem} % https://tex.stackexchange.com/questions/10684/vertical-space-in-lists
\setlist{noitemsep}
% \setlist{nosep}
\setlist[itemize]{leftmargin=*} % https://tex.stackexchange.com/questions/91124/itemize-removing-natural-indent

\begin{document}

\name{Pinglei Guo}
\centerline{
	Vancouver, BC, Canada\ \
	\href{plguo002@gmail.com}{plguo002@gmail.com}\ \
	\href{https://www.linkedin.com/in/at1510086}{linkedin.com/in/at1510086}\ \
	\href{https://github.com/at15}{github.com/at15}\ \
	\href{https://at15.dev}{at15.dev}\ \
}
\section{Work Experience}

\datedsubsection{\textbf{AWS}: Software Engineer - Amazon CloudWatch and X-Ray}{Vancouver, Canada \quad Sep 2020 - Present \quad}
\begin{itemize}
	\item Led a team of 6 engineers to implement W3C trace ID support in AWS X-Ray.
	Refactored data sharding and indexing logic to remove X-Ray trace ID timestamp dependency, unblocking 20,000 AWS accounts and enabling OpenTelemetry integration.
	\item Automated on-call investigation using AWS Bedrock by indexing runbooks and incidents into OpenSearch for RAG and creating an agent to execute common runbook commands. Reduced average investigation time from 20 to 5 minutes.
	\item Collaborated with Lambda and Application Signals teams to integrate OpenTelemetry in X-Ray ingestion API. Reduced Python Lambda function cold start time by 60\% by removing OpenTelemetry collector from the Lambda layer.
	\item Designed and implemented conversion logic between OpenTelemetry trace spans, 
	\href{https://docs.aws.amazon.com/xray/latest/devguide/xray-api-segmentdocuments.html}{X-Ray segments} and 
	\href{https://docs.aws.amazon.com/AmazonCloudWatch/latest/monitoring/CloudWatch-Transaction-Search.html}{CloudWatch transaction search log events},
	reducing customer trace data storage cost by 70\% and enabling 100\% trace sampling.
	%\item Improved X-Ray index volume by 5x by implementing proactive shard auto-scaling.
\end{itemize}

\datedsubsection{\textbf{AWS}: Software Engineer - CloudWatch Agent and OpenTelemetry distro}{Vancouver, Canada \quad Sep 2020 - July 2021 \quad}
\begin{itemize}
	\item Maintainer of open source projects on GitHub: \href{https://github.com/aws/amazon-cloudwatch-agent}{Amazon CloudWatch Agent} and \href{https://github.com/aws-observability/aws-otel-collector}{Amazon Distro of OpenTelemetry Collector}.
	\item Developed the \href{https://github.com/open-telemetry/opentelemetry-collector-contrib/tree/main/extension/observer/ecsobserver}{ECS extension} for \href{https://github.com/open-telemetry/opentelemetry-collector-contrib}{OpenTelemetry Collector},
	enabling Prometheus discovery with metadata from ControlPlane.
	\item Created Kubernetes operator to shard Prometheus scrape targets dynamically based on load instead of static hashmod in hackathon.
	Contributed to OpenTelemetry Collector Operator as \href{https://github.com/open-telemetry/opentelemetry-operator/tree/main/cmd/otel-allocator}{Target Allocator} and used in EKS addon.
\end{itemize}

\datedsubsection{\textbf{Google}: Software Engineer - Batch job on Kubernetes}{Sunnyvale, CA \quad May 2019 - Nov. 2019 \quad}
\begin{itemize}
	\item Eliminated 5\% job loss rate during controller deployment by optimizing the sequence of database updates and job submissions.
	\item Reduced debug session startup latency from 2 minutes to 40 seconds using on-demand artifact loading from object store.
\end{itemize}

\datedsubsection{\textbf{PayPal}: Software Engineer - Multi cluster container orchestration platform in Go}{San Jose, CA \quad May 2018 - May 2019 \quad}
\begin{itemize}
	%\item Worked on internal multi cloud container orchestration platform using Apache Mesos, Aurora, Docker and Cassandra.
	\item Developed a Go-based monitoring tool to correlate logs, metrics, and traces during deployment failures, automating root cause identification and reducing on-call debug time from 10 minutes to 2 minutes.
	\item Introduced a canary deployment strategy and dependency readiness checks, reducing deployment rollback ratio by 20\%.
	% TODO: number? I think I mentioned this because this is k8s crd, which is also what I did in Google ...
	%\item Built Kubernetes operator for running stateful services like database with in house underlay container network solution.
\end{itemize}

% intern time at PayPal no longer matters after working for so many years
% \datedsubsection{\textbf{PayPal}: Software Engineer Intern - Admin Server \& Dashboard in Go}{San Jose, CA \quad June 2017 - Sep. 2017}
% \begin{itemize}
% 	\item Built API gateway with role based auth (RBAC) for internal container platform using Go.
% 	\item Designed a reusable dynamic table component with filter and sort in Typescript, reducing redundant code by 90\%.
% 	% \item Introduced full text search using Apache Solr, wrote an open sourced Go client with cleaner API. % well, no longer maintained
% \end{itemize}

% sorry GitCafe, the space on resume is limited
% \datedsubsection{GitCafe: Software Engineer Intern}{Shanghai, China \quad Jan. 2015 -- Mar. 2015}
% \begin{itemize}
% 	% \setlength\itemsep{0.1em}
% 	\item Reduced \textbf{Ruby on Rails} application load time by 5\% through optimizing regular expression in markdown parser.
% 	\item Fixed user subsubcription logic, solved 20\% pricing related user tickets.
% \end{itemize}

% Yet I still love dyweb
\datedsubsection{Dongyue Web Studio at SJTU: (Part-time) Full stack web developer \& Tech lead}{Shanghai, China \quad Sep. 2013 -- Jan. 2016}
\begin{itemize}
	% Used and complained by thousands of students ...
	\item Led web and mobile teams to redesign the online event booking website \href{https://tongqu.me}{tongqu.me},
	implementing a REST API and single-page application using AngularJS.
	Reduced codebase size by 60\% and improved page load time by 80\%.
	\item Implemented a Redis and MySQL based queue system to handle ticket rushes, preventing website crashes and ticket overselling, while supporting 5x more traffic.
\end{itemize}

\section{Project Experience}

% \datedsubsection{\textbf{Go util library collection} \quad \href{https://github.com/dyweb/gommon}{github.com/dyweb/gommon}}{Open source side project \quad March. 2018 -- Present}

% \begin{itemize}
% 	\item Built a high performance structured logging library with fine grained control across libraries.
% \end{itemize}

\datedsubsection{\textbf{Distributed database benchmark tracker} \quad \href{https://github.com/benchhub}{github.com/benchhub}}{UCSC \quad 2017 -- 2018}

\begin{itemize}
	\item Designed configuration for running database benchmark for different RDBMS and TSDB in distributed environment.
	\item Built a CI service to store benchmark results in databases for performance regression detection
\end{itemize}

\datedsubsection{\textbf{Distributed Time Series Database} \quad \href{https://github.com/xephonhq/xephon-k}{github.com/xephonhq/xephon-k}}{UCSC \quad 2016 -- 2018}

\begin{itemize}
	% TODO: number, what's the TPS, what's the compression ratio, TBH I don't think I need them anymore
	\item Implemented a distributed time series database on top of Cassandra in Go. Support both JSON and Protobuf over HTTP/2.
	\item Designed a columnar storage engine modeled after Parquet and InfluxDB with high compression and less write amplification.
	\item Created a benchmark suite for OpenTSDB, KariosDB, InfluxDB with a generic interface to support different TSDB.
	\item Published a comprehensive report on TSDB design and implementation \href{https://xephonhq.github.io/awesome-time-series-database}{awesome-time-series-database}.
\end{itemize}

% \datedsubsection{\textbf{GPU accelerated in-memory time series processing} \quad \href{https://github.com/at15/ts-parallel}{github.com/at15/ts-parallel}}{UCSC \quad Apr. 2017 -- June 2017}

% \begin{itemize}
% 	\item Expanded benchmark suite for different C++ GPU computing framework on CUDA and OpenCL, Thrust, Boost, ArrayFire.
% 	\item Implemented OLAP queries like top-K, group by for multi dimensional time series data on both CPU and GPU backends.
% \end{itemize}

% \datedsubsection{\textbf{Distributed systems monitoring prototype}}{Shanghai Jiao Tong University \quad Mar. 2015 -- Jan. 2016}

% \begin{itemize}
% 	% \setlength\itemsep{0.1em}
% 	\item Enhanced monitoring system for distributed system using Cassandra and MongoDB written in Java and C++.
% 	\item Deployed in China Telecom's Kafka cluster, detected anomaly in disk and memory usage, improved capacity planning.
% \end{itemize}

% \datedsubsection{B+ index for \textbf{Hive}}{Shanghai Jiao Tong University \quad Nov. 2015 - Jan. 2016}

% \begin{itemize}
%   % \setlength\itemsep{0.1em}
%   \item Implemented B+ index for Hive, index is generated using MapReduce and stored in HDFS.
%   \item Accelerated point and range query using in memory LRU cache, supporting external cache like Memcached and Redis.
% \end{itemize}

\section{Education}
% FIXME: Package hyperref Warning: Token not allowed in a PDF string (Unicode) , caused by use \quad
\datedsubsection{MS. Computer Science \quad University of California Santa Cruz}{Sep. 2016 -- Mar. 2018}
\datedsubsection{BS. \ Materials Science \quad \ Shanghai Jiao Tong University}{Sep. 2012 -- June 2016}

\section{Skills}
% https://tex.stackexchange.com/questions/16258/how-can-the-margins-around-a-table-set-to-0pt
\begin{flushleft}
	\begin{tabular}{@{}ll@{}}
		Programming Languages  & Go, Java, TypeScript, JavaScript, Python, Dart, Rust, SQL \\
		Cloud and Infra     & AWS, GCP, Cloudflare, Kubernetes, Docker, CDK, Terraform, Prometheus, Grafana \\
		Databases  & DynamoDB, Cassandra, MySQL, PostgreSQL, Elasticsearch, OpenSearch, Redis  \\
		Frameworks & gRPC, React, Next.js, Spring \\
	\end{tabular}
\end{flushleft}

\end{document}
