% TODO: letterpaper, a4paper
\documentclass[10pt, letterpaper]{simple-cv}
\usepackage{fontawesome}

\begin{document}

\name{Pinglei Guo}
\centerline{\faMobile\ 831-295-1214\ \
\href{mailto:piguo@ucsc.edu}{\faEnvelope\ piguo@ucsc.edu}\ \
\href{https://at15.github.io}{\faHome\ at15.github.io}\ \
\href{https://github.com/at15}{\faGithubSquare\ at15}\ \
\href{https://www.linkedin.com/in/at1510086}{\faLinkedinSquare\ at1510086}}

\section{Education}
\datedsubsection{\textbf{MS. Computer Science} University of California Santa Cruz}{\textit{Sep. 2016 -- June 2018}}
\datedsubsection{\textbf{BS. Material Science} Shanghai Jiao Tong University}{\textit{Sep. 2012 -- June 2016}}

\section{Programming language}
\begin{tabular}{ l l }
 Experienced & Golang, Java, JavaScript (Node.JS), PHP, HTML, CSS \\
 Intermediate & Python, Shell, SQL, C\#, Ruby,  Scala \\
\end{tabular}

\section{Software \& Frameworks}
\begin{tabular}{ l l }
 Experienced & Git, Laravel, Express, AngularJS, jQuery, BootStrap, Vagrant \\
 Intermediate & MySQL, Redis, MongoDB, ElasticSearch, Rails, Dropwizard, Spring, ASP.NET  \\
 Basic & Docker, Mesos, Kubernetes, Cassandra, Kafka, Ceph, Hadoop, HBase, Hive, Netty
\end{tabular}

\section{Experience}
\datedsubsection{Systems Research Lab: Research assistant}{UC Santa Cruz \textit{Oct. 2016 -- Present}}
\begin{itemize}
\item Building a \textbf{hybrid distributed time series and graph database} for OLAP as master thesis
\item Validating distributed systems' (ie: Ceph) correctness by extending Jepsen
\end{itemize}

\datedsubsection{SJTU CIT Lab: Research assistant}{Shanghai, China \textit{Mar. 2015 -- Jan. 2016}}
\begin{itemize}
\item Built a distributed system monitoring and predicting prototype using \textbf{Cassandra} and \textbf{ElasticSearch}
\item Found memory bug in China Telecom's production Storm Cluster using the prototype
\item Coauthored the paper \textit{\href{https://at15.github.io/pub/cpu_load_prediction.pdf}{CPU load Prediction based on a multidimensional spatial voting model}}
\end{itemize}

\datedsubsection{GitCafe: Software Engineer Intern}{Shanghai, China \textit{Jan. 2016 -- Mar. 2016}}
\begin{itemize}
\item Built web application using \textbf{Rails} and \textbf{AngularJS}. Use \textbf{ElasticSearch} and \textbf{MongoDB} as backend storage.
\item Optimized markdown parser, added support for todo and increased 10\% speed.
\end{itemize}

\datedsubsection{Dongyue Web Studio: Full stack web developer \& President}{Shanghai, China \textit{Sep. 2013 -- Mar. 2016}}
\begin{itemize}
\item Lead web and mobile development of \url{http://tongqu.me} daily active user \textbf{increased from 500 to 3,000}.
\item Handle \textbf{high concurrency} by using Redis for cache and rate limit, increase QPS by 120\% for hot events
\item Added functionality of booking movie tickets and sports venues, integrate with Alipay for \textbf{online payment}
\item Built internal \textbf{continuous} test and deploy system around \textbf{GitLab} and GitLab CI using \textbf{container}.
\item Built \textbf{RESTful API} and rich internet application using Laravel, AngularJS and BootStrap
\end{itemize}

\section{Project}

\datedsubsection{Xephon-B: Time series database benchmark suite: Project Leader}{UC Santa Cruz \textit{Oct. 2016 -- Present}}
\begin{itemize}
\item \url{https://github.com/xephonhq/xephon-b} is a benchmark suite for \textbf{distributed time series databases}.
\item A platform where developers and vendors can share and compare benchmark result vertically and horizontally.
\end{itemize}

% TODO: this won't fix into the letter paper
% \datedsubsection{Scala-linter: Project Leader}{Shanghai, China \textit{Mar. 2015 -- June 2015}}
% \begin{itemize}
% \item \url{https://github.com/at15/scala-linter} is a compiler plugin that checks dead code and generate report.
% \item contributed to Scala official documentation
% \end{itemize}
\end{document}
